Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-29 2016-Weak-FH-Bisim/WeakBisim.tex
part 2

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
\TODO{changer alpha...}
where\\
$
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\, \wedge\\
~~\hspace{5.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
\Big) \\       
          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\set{\beta}},\Pred\,',\Post\,'   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
          \vis{\set{\beta}} \dotcup \set{\gamma},
		\Pred\,'',\Id(s'')
				 } 
         {s \OTWeakarrow {\alpha} s''} \in\WT
} \WTTrois
\end{mathpar}

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$

@@

\end{mathpar}
there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
 \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x\land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\big)$\\
and  suppose the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1},\Pred^1,\Post^1   }
         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_0^1,t|\Pred_{s_0^1,t})\in\mathcal{R}$, since $s=s_0^1$. By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1|\beta^1_j\neq\tau\}, (s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j \in J_2},\Pred\,^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} 
\end{mathpar}
For each of the weak open transition obtained above, we have the following.
We have $(s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$, then $(s_0^2,t_x|\Pred_{s_0^2,t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta^2_j\neq\tau\}, 
(s_1^2,t_{x y}|\Pred_{s_1^2,t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_1^1,t_x} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta^2_j}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$

\item 
And similarly, for the third  open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3},\Pred^3,\Post^3   }
         {s_0^3 \OTarrow {\tau} s_1^3} \in \mathcal{T}          
\end{mathpar}
Additionally, we have 
$(s_1^2,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$, then $(s_0^3,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$
and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta^3_j\neq\tau\}, 
(s^3_1,t_{x y z}|\Pred_{s_1^3,t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s_1^2,t_{x y}} \land \Pred^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{xyz}. \vis{\beta^3_j}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
     \land\! \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$

@@

\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}

@@

		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}}\subst{\Post_{OT_{x}}}}  

@@

\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$

>>>>

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
\TODO{changer alpha...}\\
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\, \wedge\\
~~\hspace{5.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
\Big) \\       
          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha'} s''} \in\WT
}
$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\set{\beta}},\Pred\,',\Post\,'   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\set{\gamma''}= \vis{\set{\beta}} \dotcup \set{\gamma}\subst{\Post\,'}\quad
\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post\,' \quad \alpha''=\alpha'\subst{\Post\,'}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s \OTWeakarrow {\alpha''} s''} \in\WT
} \WTTrois
\end{mathpar}

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)}$

@@

\end{mathpar}
there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
 \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x\land  
     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^1},\Pred^1,\Post^1   }
         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_0^1,t|\Pred_{s_0^1,t})\in\mathcal{R}$, since $s=s_0^1$. By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1|\beta^1_j\neq\tau\}, (s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred^1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j \in J_2},\Pred\,^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} 
\end{mathpar}
For each of the weak open transition obtained above, we have the following.
We have $(s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$, then $(s_0^2,t_x|\Pred_{s_0^2,t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta^2_j\neq\tau\}, 
(s_1^2,t_{x y}|\Pred_{s_1^2,t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_1^1,t_x} \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta^2_j}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}}\right)$

\item 
And similarly, for the third  open transition:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \set{\beta^3},\Pred^3,\Post^3   }
         {s_0^3 \OTarrow {\tau} s_1^3} \in \mathcal{T}          
\end{mathpar}
Additionally, we have 
$(s_1^2,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$, then $(s_0^3,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$
and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta^3_j\neq\tau\}, 
(s^3_1,t_{x y z}|\Pred_{s_1^3,t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s_1^2,t_{x y}} \land \Pred^3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{xyz}. \vis{\beta^3_j}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
     \land\! \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3\shortotimes\Post_{OT_{x y z}}}\right)$

@@

\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}

@@

		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}}}  

@@

\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
